### 2021-11-16 input/proposal.tex
meow

\begin{definition}[\label{def:lwo}Message staleness]
  Only the latest message of a \process matters. A message $m$ conveys
  \underline{s}tale control information if the \process that broadcast
  $m$ later broadcast another message $m'$: $S(m) = \exists m': b_p(m)
  \rightarrow b_p(m')$.

@@

\begin{definition}[\label{def:purge}Message purge]
  A system purges a message \TODO{$P(m)$} when every \node $q$ that
  delivered $m$ eventually delivers another message $m'$ never
  followed by the delivery of the former message $m$: $d_q(m) \implies
  \eventually (d_q(m) \rightarrow d_q(m')) \TODO{\wedge}$.
\end{definition}

\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
  to ensure consistent partitioning, eventual forwarding of best
  (Theorem~\ref{theo:efb}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m) \implies P(m)$), then
\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
\end{inparaenum}
\end{theorem}

>>>>

\begin{definition}[\label{def:lwo}Message staleness]
  Only the latest message of a \process matters. A message $m$ conveys
  \underline{s}tale control information if the \process that broadcast
  $m$ later broadcast another message $m'$: $\mathcal{S}(m)
  = \exists m': b_p(m) \rightarrow b_p(m')$.

@@

\begin{definition}[\label{def:purge}Message purge]
  A system \underline{p}urges a message $\mathcal{P}(m)$ when every
  \node $q$ that delivered $m$ eventually delivers another message
  $m'$ never followed by the delivery of the former message $m$:
  $d_q(m) \implies \exists m': \eventually (d_q(m)
  \rightarrow d_q(m') \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
\end{definition}

\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
  to ensure consistent partitioning, eventual forwarding of best
  (Theorem~\ref{theo:efb}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($\mathcal{S}(m) \implies
  \mathcal{P}(m)$), then
\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
\end{inparaenum}
\end{theorem}
